Crunching Large Graphs with Commodity Processors

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
crash recovery

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, Andrew Hunter, Dan Grossman, Mark Oskin,
Carl Ebeling, Luis Ceze}{University of Washington}{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}
\authorinfo{Simon Kahan}{Pacific Northwest National Lab}{skahan@cs.washington.edu}
\authorinfo{Preston Briggs}{}{preston.briggs@gmail.com}

\maketitle
\begin{abstract}

 Techniques from graph analytics have found important applications in
  areas such as social networks and bioinformatics. These irregular
  problems present a challenge for parallel machines: obtaining
  performance is not straightforward. Multithreading works well for
  such problems, but the only large-scale implementation of the technique
  is the Cray XMT, an expensive, non-commodity machine.

  Our goal is to build a system with XMT-like properties, implemented
  with commodity components. This paper presents a runtime for latency
  tolerance, along with our plans for scaling up to multiple
  nodes. Our analysis shows the feasibility of our approach.
\end{abstract}

@@

Techniques from graph analytics have found important applications in
areas such as social networks and bioinformatics. \todo{more}

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{figures/system-overview.pdf}
	\end{center}
	\caption{Overview of our proposed system design. The base
          system is a cluster of commodity nodes and interconnect. We
          add a latency-tolerant runtime and a global memory manager
          to obtain efficient access to the global address space. Only
          the shaded components may require hardware design.}
	\label{fig:system-overview}
\end{figure*}

>>>>

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, A.H. Hunter, Preston Briggs,
  Dan Grossman, Mark Oskin, Carl Ebeling, Simon Kahan, Luis
  Ceze}{University of Washington}{\{nelson, bdmyers, ahh, preston,
  djg, oskin, ebeling, skahan, luisceze\}@cs.washington.edu}

\maketitle

\begin{abstract}
   Crunching large graphs is the basis of many emerging applications,
   such as social network analysis and bioinformatics. Graph analytics
   algorithms exhibit little locality and therefore present significant
   performance challenges. Hardware multithreading systems (e.g, Cray
   XMT) showed that with enough concurrency, we can tolerate long
   latencies. Unfortunately, this solution is not available with
   commodity parts.

   Our goal is to develop a latency-tolerant system built out of
   commodity parts and mostly in software. The proposed system includes
   a runtime that supports a large number of lightweight contexts,
   full-empty synchronization and a memory manager that provides a
   high-latency but high-bandwidth global shared memory. This paper
   lays out the vision for our system, and justifies its feasibility
   with a performance analysis of the runtime for latency tolerance.

\end{abstract}

@@

Many important emerging applications such as social network analysis,
bioinformatics and analysing vast sensor data from actual networks
(e.g, water, electrical grid) are based on crunching very large
graphs. Unfortunately, the computational cost of these applications
gets quickly out of hand. For example, in January 2011, Facebook had
500 million active users with an average of 130 friends each
\cite{Facebook:2011p91}. Its friend suggestion algorithm in 2010 ran on
  a 40-node cluster with 72GB memory per node, and still, new
  suggestions could only be computed every two days
  \cite{Backstrom:2010p90}. Speeding up these applications at a low
  cost would have a large impact in how we deal and react to the fast
  growth of the data-set and would make the results even more
  valuable.

@@

\begin{figure*}[htbp]
  \begin{center}
    \vspace{-0.25in}
    \includegraphics[width=0.7\textwidth]{figures/system-overview.pdf}
    \vspace{-0.2in}
	\end{center}
	\caption{Overview of our proposed system design. The base
          system is a cluster of commodity nodes and interconnect. We
          add a latency-tolerant runtime and a global memory manager
          to obtain efficient access to the global address space. Only
          the shaded components may require hardware design.}
	\label{fig:system-overview}
\end{figure*}
